Radiocarbon measurement of CO~2~ from carbonate minerals using a gas ion source with an open split interface

### 2021-10-21 doc/AMS-15/AMS-15_poster.Rmd
Fix superscripts in plot axis labels

```{r}
library(tidyverse)
library(amstools)
library(hgis)
library(here)
library(gt)
library(Bchron)
library(gghighlight)
library(patchwork)
library(scales)

@@

```{r cur-flow-os}
ggplot(data, aes(co2flow, he12C)) +
  geom_smooth(span = .3, se=FALSE, color = "#00b7bd") +
  geom_point(size = 2, color = "#0069b1") +
  labs(title = bquote('Ion current is stable for a range of CO'[2]~'flow'),
       subtitle = bquote('Current vs. CO'[2]~'flow during vial dillution'),
       x = bquote('CO'[2]~'Flow (μl/min)'), 
       y = "12C current (μA)") +
  theme_classic()
```

@@

```{r blanks}
cons_df %>% 
  filter(fm_consensus < 0.1) %>% 
  ggplot(aes(he12C, norm_ratio)) +
  geom_errorbar(aes(ymin = norm_ratio - sig_norm_ratio, ymax = norm_ratio  + sig_norm_ratio)) +
  geom_errorbarh(aes(xmin = he12C - sig_he12C, xmax = he12C  + sig_he12C)) +
  geom_point(size = 2, color = "#0069b1") + #"#b7bf10"
  #scale_color_manual("wheel", values = c("#b7bf10", "#00a9e0", "#0069b1")) +
  scale_y_continuous(breaks = breaks_extended(7),
                     labels = label_percent(suffix = "",
                                            accuracy = 1)) +
  labs(title = "Contaminant carbon is related to current",
       subtitle = "Fm and current of radiocarbon-free carbonates",
       x = "12C Current (μA)",
       y = "pMC") +
  theme_classic() +
  theme(legend.position = c(0.82, 0.76),
        legend.background = element_rect(fill = "white", color = "black")) 
```

>>>>

```{r}
library(tidyverse)
library(amstools)
library(hgis)
library(here)
library(gt)
library(Bchron)
library(gghighlight)
library(patchwork)
library(scales)
library(latex2exp)

@@

```{r cur-flow-os}
ggplot(data, aes(co2flow, he12C)) +
  geom_smooth(span = .3, se=FALSE, color = "#00b7bd") +
  geom_point(size = 2, color = "#0069b1") +
  labs(title = bquote('Ion current is stable for a range of CO'[2]~'flow'),
       subtitle = bquote('Current vs. CO'[2]~'flow during vial dillution'),
       x = bquote('CO'[2]~'Flow (μl/min)'), 
       y = TeX(r'(^{12}C^- current (μA))')) +
  theme_classic()
```

@@

```{r blanks}
cons_df %>% 
  filter(fm_consensus < 0.1) %>% 
  ggplot(aes(he12C, norm_ratio)) +
  geom_errorbar(aes(ymin = norm_ratio - sig_norm_ratio, ymax = norm_ratio  + sig_norm_ratio)) +
  geom_errorbarh(aes(xmin = he12C - sig_he12C, xmax = he12C  + sig_he12C)) +
  geom_point(size = 2, color = "#0069b1") + #"#b7bf10"
  #scale_color_manual("wheel", values = c("#b7bf10", "#00a9e0", "#0069b1")) +
  scale_y_continuous(breaks = breaks_extended(7),
                     labels = label_percent(suffix = "",
                                            accuracy = 1)) +
  labs(title = "Contaminant carbon is related to current",
       subtitle = "Fm and current of radiocarbon-free carbonates",
       x = TeX(r'(^{12}C^- current (μA))'),
       y = "pMC") +
  theme_classic() +
  theme(legend.position = c(0.82, 0.76),
        legend.background = element_rect(fill = "white", color = "black")) 
```
